
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.


\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
\usepackage{mathptmx} % assumes new font selection scheme installed
\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed

\usepackage[font=small,labelfont=bf]{caption}

% Other package
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{caption} 
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{array}
\usepackage{booktabs}
\usepackage{hyperref}

\usepackage{pdfpages}
\usepackage{caption}
%\usepackage{geometry}
\usepackage{import}
\usepackage{standalone}

\title{\LARGE \bf
  Team-JSK: MBZIRC Progress Report
}
\author{Team JSK$^\dagger$% <-this % stops a space
  \\ JSK Lab, Graduate School of Information Science and Technology, The University of Tokyo \\
  7-3-1 Hongo, Bunkyo-ku, Tokyo 113-8656, Japan.  \\
{\tt\small mbzirc-team@jsk.imi.i.u-tokyo.ac.jp}
\thanks{$^{*}$ %JSK Lab, Graduate School of Information Science and Technology, The University of Tokyo,  7-3-1 Hongo, Bunkyo-ku, Tokyo 113-8656, Japan.  
{$^\dagger$\tt\small \url{http://www.jsk.t.u-tokyo.ac.jp}}
}}
\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}


\section{Introduction}
This document provides a report of Team JSK’s progress in preparing for the Mohamed Bin Zayed International Robotics Challenge (MBZIRC). The team consists of members from the JSK Laboratory at the University of Tokyo. The JSK Lab, founded in early 1980’s, has a long history of robotics research with focus on areas including humanoids, drones, robotics manipulation, and perception. The lab has experience in participating in robotics challenges including the DARPA Robotic Challenge and the Amazon Picking Challenge.

\section{Project Personnel}
Team JSK is made of 11 members. The 11 members are Prof. Inaba, Prof. Okada, Dr. Kakiuchi, Dr. W. Chan, Bakui Chou, Xiangyu Chen, Krishneel Chaudhary, Kohei Kimura, Yuki Furuta and Hiroto Mizohana. The team is divided into 3 groups generally to handle various tasks such as software and hardware developments and other project related activities. All team members are from JSK Lab, in The University of Tokyo.

%That is a professor, a associate-professor, a lecturer, a researcher, 4 Phd students and 2 Master students. 
%Teachers mainly focus on manage the whole team schedule, design hardware and software architecture, provide advices and give ideas for all the tasks. The rest researcher and students are divided into three groups, 
%one for computer vision development for all the tasks, one for task 2 and one for task 1 and 3.



\section{CHALLENGE 1: LANDING UAV ON A MOVING VEHICLE}

\input{sections/task1/software.tex}
\input{sections/task1/hardware.tex}
%% insert yout latex module file here. the contents should go to the tasks folder under section

\section{CHALLENGE 2: OPERATING A VALVE STEM}
\input{sections/task2/software.tex}

\section{CHALLENGE 3: SEARCH, PICK AND PLACE}


\input{sections/task3/example.tex}

\section{GRAND CHALLENGE}


\section{Future Plan}

\end{document}